Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-08 paper/snakemajoranas.tex
rewrite the abstract and section I

\date{\today}
\begin{abstract}
We solve the problem of the appearance of a soft gap in high-density SNS Majorana junctions \cite{pientka2017topological}.
Trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
A small induced gap then becomes an essential obstacle in creating Majorana states.
We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
\end{abstract}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}

\comment{Majoranas are mostly made in hybrid NS structures.}
The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a long strip (or wire) of a semiconductor is interfaced with a superconductor.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological while MBSs appear at the ends of the segment.

\comment{A alternative has been proposed (JJ).}
Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
Currently, proposed workarounds are to work at low density \cite{nijholt2015orbital} or to have disorder~\cite{haim_double-edge_2018}, but both have drawbacks.  % TODO: mention drawbacks?

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
In this paper, we show that introducing a zigzag or snake-like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.

@@

\comment{We consider a two-dimensional system with zigzag.}
We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
The complete Hamiltonian has the form
\begin{equation}
\begin{split}
    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
        & + E_\text{z}(x,y) \sigma_x \\
        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
          + \Delta(x,y) \tau_y.
\end{split}
\label{eq:hamiltonian}
\end{equation}
It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.

>>>>

\date{\today}
\begin{abstract}
Quasi-particle trajectories in high density SNS junctions that have a large momentum parallel to the junction have a very long flight time.
These trajectories that do not encounter the superconductor for a long time weaken the proximity effect in Josephson junctions.
This results in a very small induced gap and a soft gap in Majorana devices.
We propose to eliminate these long trajectories using a new Majorana device.
We show that a zigzag-shaped geometry eliminates these trajectories, at the same time allowing the robust creation of Majorana states with a gap increased by more than an order of magnitude and a significantly reduced Majorana decay length.
Further, we show that to exploit the benefits of this system, the details exact of the geometry are not important.
\end{abstract}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple nanowire), while Majorana bound states appear on its edges.~\cite{lutchyn_majorana_2010,oreg_helical_2010}
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{alicea2012new,beenakker2013search}
The current experimental effort ~\cite{mourik_signatures_2012,das_zero-bias_2012,deng_anomalous_2012,churchill_superconductor-nanowire_2013,zhang2018quantized} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowires structures.

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap~\cite{ren_topological_2018}; where the gap in the density of states significantly reduces for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f=v_F(\theta) / D$ (see Fig.~\ref{fig:setup}(a)) and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap. % TODO: fix the Eq for tau_f
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, so a low filling of the bands is a workaround\cite{nijholt2015orbital}.
However, low filling requires precise knowledge of the system and might be more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cut-off on the scale of the mean-free path~\cite{haim_double-edge_2018}, however, disorder is impossible to control to a required precision experimentally.

\comment{A alternative has been proposed.}
Recently, a system with a modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
The additional superconductor adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
Recently, two groups~\cite{fornieri_evidence_2018,ren_topological_2018} have realized this system experimentally.
In practice, multiple problems arise making even the observation difficult, rendering the manipulation of Majoranas in the near future, improbable.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We propose a new experimental setup (see Fig.~\ref{fig:setup}(b)) for the creation of Majoranas that eliminating long trajectories and therefore prevents the appearance of a soft gap, while while also increasing the topological gap by several orders of magnitude, depending on the parameters.
The setup consists of a zigzag or snake-like geometry for the semiconductor where long trajectories are not possible due to the geometry.

@@

\comment{We consider a two-dimensional system with zigzag.}
We consider a Josephson junction (Fig.~\ref{fig:setup}) consisting of a two-dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal-like shape.
Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a Bogoliubov-de Gennes Hamiltonian (BdG) Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2} \mu_B g B_x$.
The superconductor has a superconducting coupling term $\Delta$ with the pair of superconductors at an opposite superconducting phase $\exp{\pm i \phi/2}$.
Both the normal part and the superconducters have a kinetic term and chemical potential $\mu$.
The complete Hamiltonian has the form
\begin{equation}
\begin{split}
    H = & \left[\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right] \tau_z \\
        & + E_\text{z}(x,y) \sigma_x \\
        & + \alpha(x,y) \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z
          + \Delta(x,y) \tau_y.
\end{split}
\label{eq:hamiltonian}
\end{equation}
It acts on the spinor wave function $\Psi={\left(\psi_{e\uparrow},\psi_{e\downarrow},\psi_{\textrm{h}\downarrow},-\psi_{\textrm{h}\uparrow}\right)}^{T}$, where $\psi_e$, $\psi_\textrm{h}$ are its electron and hole components, and $\psi_\uparrow$, $\psi_\downarrow$ are the spin-up and spin-down components.
The Pauli matrices $\sigma_{i}$ act on the spin degree of freedom and $\tau_{i}$ act on the electron-hole degree of freedom.
For the zigzag geometry, we first consider a sawtooth-like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
The spatial dependence of $\Delta$, $E_z$, and $\alpha$ is explained in text above.
Later in this manuscript, we show that the exact details of the shape are unimportant and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.
